Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-03-23 data_appendix.Rmd
Added structure for creating a dept variable that has the name of the department instead of the number to facilitate matching with the flood and drought data
Added structure in the flood section that will read in all variables and flip the data. The same structure needs to be followed in the drought section.

```{r import household data}
data_2005 <- read_dta(file.path("Raw data","seminar_paper_data","2005_hhsurvey.dta")) %>% 
  rename(hh_id = folio,
        assist = s3_08,  
        reason = s3_09, 
        members = nm_y,
        sex = s1_02,
        age = s1_03,
        relation = s1_05,
        literacy = s3_01,
        register = s3_04,
        grade = s3_05b,
        repeated = s3_07,
        dept = depto)
hh_2005 <- data_2005 %>% 
  select(hh_id, assist, reason, members, sex, age, relation, literacy, register, grade, repeated, dept, urb_rur)
```

@@

### Data import code and summary
```{r import flood data}
flood <- read_csv(file.path("Raw data", "recurrencia_inundacion2002_2012bol.csv")) %>% 
  rename(dept = NOM_DEP, flood = A_2005)

flood_summary %>% weather %>% 
  group_by(dept) %>% 
  summarise(flood = sum(flood))

`export_summary_table(dfSummary(flood_summary))`
```
## Drought data
**Citation:** GeoSinager. (2016). Mapa Recurrencias de Sequias Gestiones 2002-2012. [CSV file]. Retrieved from http://geosinager.defensacivil.gob.bo/maps/225

@@

```{r importing droughts data, echo = F, message = F}
#drought data set 
library(readxl)
drought <- read_excel(file.path("Raw data", "recurrenciasequia_2002_2012bol (1).xls")) %>% 
#rename variables
    rename(dept = NOM_DEP, drought = A_2005)
drought_summary %>%
  group_by(dept) %>% 
  summarise(flood = sum(flood))

`export_summary_table(dfSummary(drought_summary))`

>>>>

```{r import household data}
data_2005 <- read_dta(file.path("Raw data","seminar_paper_data","2005_hhsurvey.dta")) %>% 
  rename(hh_id = folio,
        assist = s3_08,  
        reason = s3_09, 
        members = nm_y,
        sex = s1_02,
        age = s1_03,
        relation = s1_05,
        literacy = s3_01,
        register = s3_04,
        grade = s3_05b,
        repeated = s3_07) %>% 
  mutate(dept = case_when(depto == "1" ~ "Department 1",
                          depto == "2" ~ "Department 2"))

hh_2005 <- data_2005 %>% 
  select(hh_id, assist, reason, members, sex, age, relation, literacy, register, grade, repeated, dept, urb_rur)
```

@@

### Data import code and summary
```{r import flood data}
flood <- read_csv(file.path("Raw data", "recurrencia_inundacion2002_2012bol.csv")) %>% 
  rename(dept = NOM_DEP)

flood_summary <- flood %>% 
  group_by(dept) %>% 
  summarize_at(vars(starts_with("A_")), sum) %>% 
  pivot_longer(-dept, names_to = "year", names_prefix = "A_", values_to = "floods")

export_summary_table(dfSummary(flood_summary))
```
## Drought data
**Citation:** GeoSinager. (2016). Mapa Recurrencias de Sequias Gestiones 2002-2012. [CSV file]. Retrieved from http://geosinager.defensacivil.gob.bo/maps/225

@@

```{r importing droughts data, echo = F, message = F}
#drought data set 
library(readxl)
drought <- read_excel(file.path("Raw data", "recurrenciasequia_2002_2012bol (1).xls")) %>% 
#rename variables
    rename(dept = NOM_DEP)

drought_summary %>%
  group_by(dept) %>% 
  summarise(flood = sum(flood))

export_summary_table(dfSummary(drought_summary))
